---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Charlize Ezernack"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
  df <- read_csv("kansas_grouped_rolling_avg.csv") 
```

### Exercise 2

```{r revisualize}
ggplot(df, aes(x = date, y = rolling_avg, color = mask_mandate)) + geom_line() + labs(title = "Kansas COVID-19 7-Day Rolling Average of Daily Cases/Per 100K Population", subtitle = "Mask Counties Vs. No-Mask Mandate Counties", caption = "Source: Kansas Department of Health and Environment", x = "Date", y = "Rolling Average", color = "Type of Mandate")

```

### Exercise 3

In the new visualization, the rolling average is depicted on one y-axis which indicates the trends more clearly than the previous dual y-axis. The new graph shows very clearly how on average, the counties with the mask mandate had higher rolling averages. 

### Exercise 4

Based on this graph, we can see that COVID-19 rates are not protected from mask mandating counties. Instead, a formal mask mandate might deter people from wearing masks since they were forced to and that might of added to higher cases of COVID-19. The visualization shows that mask mandating counties have significantly more cases on a 7 day rolling basis. From my own personal experience in a mask mandating county, a lot of people still wore masks to school and such, but people tended to incorrectly wear them. Hence, I think Covid-19 cases is less about the mandate itself, but more how individuals on average comply with maintaining safe practices. 

Add exercise headings as needed.
