---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Charlize Ezernack"
date: "03-01-2026"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
  df <- read_csv("kansas_grouped_rolling_avg.csv") 
```

### Exercise 2

```{r revisualize}
ggplot(df, aes(x = date, y = rolling_avg, color = mask_mandate)) + geom_line() + labs(title = "Kansas COVID-19 7-Day Rolling Average of Daily Cases/Per 100K Population", subtitle = "Mask Counties Vs. No-Mask Mandate Counties", caption = "Source: Kansas Department of Health and Environment", x = "Date", y = "Rolling Average", color = "Type of Mandate")

```

### Exercise 3

In the new visualization, the rolling average is depicted on one y-axis which indicates the trends more clearly than the previous dual y-axis. The new graph shows very clearly how mandates decreased the amount of average cases of COVID-19. 

### Exercise 4

Based on this graph, we can see that COVID-19 rates are protected from mask mandating counties. There was a significant drop once mask mandates were introduced, and masks helped to stabilize the amount of cases within these counties. 

### Exercise 5

The variables used in this visualization are dates, rolling average of cases, and mandate. The current variables used convey the message that mask mandates helped decrease the amount of daily cases. Especially with the line graph, we can see the huge drop occuring in cases in counties with the mandate vs those with the mandate. However, because of the scale of the y axis, it mainly focuses on this drop, and not really how the mask mandated counties still contain higher cases on average. In my personal experience, a formal mask mandate might deter people from wearing masks since they were forced to and that might of added to higher cases of COVID-19.  


### Exercise 6

I want to convey that even though there was a drop after the introduction of mask-mandates, the rates of cases are still higher than the counties with no mask mandates. The visualization should reflect that mask mandating counties have significantly more cases on a 7 day rolling basis. From my own personal experience in a mask mandating county, a lot of people still wore masks to school and such, but people tended to incorrectly wear them. Hence, I think the amount of Covid-19 cases is less about the mandate itself, but more how individuals on average comply with maintaining safe practices. To do so I will filter out the outlier of 24 cases.  

### Exercise 7
```{r revisualize2}
df %>% filter(rolling_avg < 20) %>% ggplot(aes(x = date, y = rolling_avg, color = mask_mandate)) + geom_line() + labs(title = "Kansas COVID-19 7-Day Rolling Average of Daily Cases/Per 100K Population", subtitle = "Mask Counties Vs. No-Mask Mandate Counties", caption = "Source: Kansas Department of Health and Environment", x = "Date", y = "Rolling Average", color = "Type of Mandate")

```

### Exercise 8
https://flowingdata.com/2014/04/16/weird-stacked-area-map-thing/ 

I found this graph to be misleading since it is trying to visualize demographics of race over the general map geographic. It makes it misleading because the audience does not know whether the distribution of race is trying to be depicted those geographic locations as well, which is just not true. 